SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2019-05-15 conc.tex
ack hprc
minor

We thank the anonymous reviewers for their valuable comments and feedback to
improve the content and quality of this paper.  We also thank the National
Science Foundation, which supports this work through grants FoMR-1823403 and
CCF-1649242.  We thank Intel Corp. for their generous support. We thank
Samsung for supporting this work through their Global Outreach Program.

>>>>

We thank the anonymous reviewers for their valuable comments and
feedback to improve the content and quality of this paper.  We also
thank the National Science Foundation, which supports this work
through grants FoMR-1823403, I/UCRC-1439722 and CCF-1649242.  We thank
Intel Corp. for their generous support. We thank Samsung for
supporting this work through their Global Outreach Program.  Portions
of this research were conducted with the advanced computing resources
provided by Texas A\&M High Performance Research Computing.
